Continuations via Negative Information Flow

### 2012-02-13 dual.tex
_

\begin{enumerate}
\item You produce a \$20.00 bill and give it to the seller.
\item You use a credit card. 
\end{enumerate}
In both cases the seller receives the money immediately but there is a subtle
difference. In the second transation, nobody has yet produced the money that
the seller has received: instead a \emph{debt} is generated and this debt
travels ``backwards'' towards the bank and (hopefully) reconciled there.

@@

The othe way is to follow the execution. It goes forward in time so to speak,
comes back, and then goes forwards again.

@@

\paragraph*{Filinski.}

@@

>>>>

\begin{enumerate}
\item You produce a \$20.00 bill and give it to the seller.
\item You use a credit card. 
\end{enumerate}
In both cases the seller receives the money immediately but there is a subtle
difference. In the second transaction, nobody has yet produced the money that
the seller has received: instead a \emph{debt} is generated and this debt
travels ``backwards'' towards the bank and (hopefully) reconciled there.

@@

The other way is to follow the execution. It goes forward in time so to speak,
comes back, and then goes forwards again.

@@

\paragraph*{Filinski~\cite{Filinski:1989:DCI:648332.755574}.}
In his Masters thesis, Filinski proposes that continuations are a
\emph{declarative} concept. He, furthermore, introduces a symmetric extension
of the $\lambda$-calculus in which values and continuations are treated as
opposites. This is essentially what we are proposing with one fundamental
difference: our underlying language is not the $\lambda$-calculus but a
language of pure isomorphisms in which information is preserved. This shift
of perspective enables us to distill and generalize the duality of values and
continuations: in particular, in the conventional $\lambda$-calculus setting
values and continuations can be erased and duplicated which makes it
difficult to maintain the correspondence between a value and its negative
counterpart. In contrast, in our setting, one can start from the empty type
$0$, introduce a positive value and its negative counterpart, and let each of
these flow in arbitrary ways. The entire framework guarantees that neither
the value nor its negative counterpart will be deleted or duplicated and
hence that, in any closed program, the ``debt'' corresponding to the negative
value is paid off exactly once.

The forward and backward executions in our framework correspond to
call-by-value and call-by-name. This duality was observed by Filinski and
others following him but it is particularly clean in our framework.

@@

\item Which operations can be lifted to work on negative types?
